---
output:
  html_document: default
  pdf_document: default
---

```{r, eval=F,include=F}
rm(list = ls())
library(tidyverse)
library(MRIcloudT1volumetrics)


roiDir = paste0(getwd(),'/data')
file_list = dir(roiDir)
# readSubjectDf(file_list[1])$level

# run it in console
# setwd("C:/Users/lcqi/Desktop/data_analysis_bcaffo_lab/MRI_data_analysis/data")
data = readFileList(fileList = file_list,fixBF = TRUE)
save(data, file = 'raw.rda')


```


# choose type and level
```{r}
# note function spreadROIs() doesn't work very well
# data = readFileList(fileList = file_list,fixBF = TRUE) %>% spreadROIs()

rm(list = ls())
library(tidyverse)
library(MRIcloudT1volumetrics)

load(file = 'raw.rda')

data = data %>% filter(type==1,level==2) %>% 
  select(rawid,roi,volume) %>% spread(roi,volume) 

# convert the rawid to be compatible with the format in lookup table
data$rawid = sapply(strsplit(data$rawid,"_"),function(x) x[1])

# compositional analysis
# data = data %>% lapply(function(x) as.numeric(x)) %>% as.data.frame
# data = cbind(data[1],prop.table(as.matrix(data[-1]), margin = 1))
# data = data[-1]


# get rid of CSF
# data = data %>% select(-Ventricle)

```




# compositional analysis
```{r}
# only Telencephalon
data = data %>% select(rawid,CerebralCortex_L,CerebralNucli_L,WhiteMatter_L,
                        CerebralCortex_R,CerebralNucli_R,WhiteMatter_R,)

# compositional analysis

# data = data %>% lapply(function(x) as.numeric(x)) %>% as.data.frame
id = data[1]
data = cbind(data[1],prop.table(as.matrix(data[-1]), margin = 1))
data = data[-1]
```




# no need to normalize for correlation?

```{r, eval=F,include=F}
library(ggplot2)


ggplot(gather(data), aes(value)) + 
    geom_histogram(bins = 10) + 
    facet_wrap(~key, scales = 'free_x')

data = apply(data, MARGIN = 2, FUN = function(i){ scale(i) }) %>% as.data.frame()

ggplot(gather(data), aes(value)) + 
    geom_histogram(bins = 10) + 
    facet_wrap(~key, scales = 'free_x')



```

```{r}
library(glasso)
library(qgraph)
gs = lapply(seq(0,0.1,0.02), function(i){
  qgraph(glasso(cov(data),rho = i),
       labels = colnames(cov(data)),
       # filetype = 'pdf',
       # filename = paste0('rho=',i),
       # layout = matrix(1:12,nrow = 4),
       # DoNotPlot = TRUE,
       details = TRUE,
       directed = TRUE)
})
```



```{r}
library(corrplot)
corrplot(cor(data, method = 'spearman'),
         # addCoef.col = T,
         method = 'color',
         type = 'upper',
         order = 'hclust',
         p.mat = cor.mtest(data, conf.level = .95)$p
         )
# interesting results of Telencephalon
library(randomForest)
lapply(colnames(data), function(i){
  # fml = paste0(i,"~.-",i) %>% as.formula()
  fml = paste0(i,"~.") %>% as.formula()
  data.rf = randomForest(fml, data, importance = TRUE)
  varImpPlot(data.rf,
             main = i)
})
```



# cor res_detailed

```{r}
# data = data.frame(id,data)
# ref = read.csv(paste0(getwd(),'/unrestricted_bcaffo_12_12_2017_12_17_8.csv%3B.csv'), header = T)
# colnames(ref)[1] = 'rawid'
# 
# data[1] = as.numeric(unlist(data[1]))
# data = left_join(data, ref[,c('rawid','Age','Gender')], by="rawid") %>% na.omit
# 
# save(data,file = 'data.Rda')
rm(list = ls())
load(file='data.Rda')
data_M = filter(data,Gender == 'M')
data_F = filter(data,Gender == 'F')



test = function(x,y){
  l1 = length(x)
  l2 = length(y)
  data = sample(c(x,y),replace = T)
  mean(data[1:l1]) - mean(data[l1:(l1+l2)])
}

sex_res = lapply(2:7, function(i){
  tr_diff = mean(data_M[i] %>% unlist ) - mean(data_F[i] %>% unlist)
  re_diff = replicate(1000, test(data_M[i]%>%unlist, data_F[i] %>% unlist))
  p_value = mean(abs(tr_diff)>=abs(re_diff))
}) %>% do.call(what='cbind') %>% as.data.frame()
colnames(sex_res) = colnames(data)[2:7]

sex_res

# t_res = lapply(2:7, function(i){
#   p_value = t.test(data_M[i]%>%unlist, data_F[i] %>% unlist)$p.value
# }) %>% do.call(what='cbind') %>% as.data.frame()
# colnames(t_res) = colnames(data)[2:7]
# 
# t_res


data22_M = data_M %>% filter(Age == '22-25')
data26_M = data_M %>% filter(Age == '26-30')
data31_M = data_M %>% filter(Age == '31-35')
data36_M = data_M %>% filter(Age == '36+')

data22_F = data_F %>% filter(Age == '22-25')
data26_F = data_F %>% filter(Age == '26-30')
data31_F = data_F %>% filter(Age == '31-35')
data36_F = data_F %>% filter(Age == '36+')

library(ggcorrplot)
vec = list('data22_M','data22_F','data26_M','data26_F','data31_M','data31_F','data36_M',
           'data36_F')
lapply(vec, function(i){
  data = get(i) %>% select(-rawid,-Age,-Gender)
  ggcorrplot(cor(data, method = 'spearman'), 
             hc.order = TRUE,
             type = "lower",
             p.mat = cor_pmat(data),
             lab = TRUE,
             title = i)
})

```


# regression model
```{r}
regression_data = data %>% select(-rawid)
# regression_data = data %>% select(-rawid,-Age,-Gender)
regression_res = list()

for (i in colnames(regression_data)[1:6]) {
  fml = paste0(i,"~.") %>% as.formula()
  model = glm(fml, family = gaussian, data = regression_data)
  regression_res[[i]] = model
}

lapply(regression_res,summary)
```




# Does spearman correlation change across age?


```{r}
rm(list = ls())
load(file = 'data.Rda')
data22 = data %>% filter(Age == '22-25')
data26 = data %>% filter(Age == '26-30')
data31 = data %>% filter(Age == '31-35')
data36 = data %>% filter(Age == '36+') 
library(ggcorrplot)
vec = list('data22','data26','data31','data36')
lapply(vec, function(i){
  data = get(i) %>% select(-rawid,-Age,-Gender)
  ggcorrplot(cor(data, method = 'spearman'), 
             hc.order = TRUE,
             type = "lower",
             p.mat = cor_pmat(data),
             lab = TRUE,
             title = i)
})
```



# permutation test(not the mean, cor efficients)

```{r}
load(file = 'data.Rda')
data22 = data %>% filter(Age == '22-25')
data26 = data %>% filter(Age == '26-30')
data31 = data %>% filter(Age == '31-35')
data36 = data %>% filter(Age == '36+')

library(gtools)
vec = combinations(4,2,c('data22','data26','data31','data36'))
age_res = list()


test = function(data1,data2,i){
  l1 = dim(data1)[1]
  l2 = dim(data2)[1]
  data = c(data1[i[1]],data1[i[2]],data2[i[1]],data2[i[2]]) %>% unlist
  #shuffle
  data = sample(data,replace = F)
  cor(data[1:l1],data[(1+l1):(2*l1)], method = 'spearman')-
    cor(data[(2*l1+1):(2*l1+l2)],data[(2*l1+l2+1):(2*l1+2*l2)], method = 'spearman')
}


roi = colnames(data)[2:7]
vec2 = combinations(length(roi),2,roi)

for(j in 1:dim(vec)[1]){
  data1 = get(vec[j,1])
  data2 = get(vec[j,2])
  perm_res = lapply(1:dim(vec2)[1], function(i){
  i = vec2[i,]
  tr_diff = cor(data1[i[1]],data1[i[2]], method = 'spearman') - cor(data2[i[1]],data2[i[2]],  method = 'spearman')
  tr_diff = tr_diff %>% as.numeric()
  re_diff = replicate(5000, test(data1,data2,i))
  # hist(re_diff)
  p_value = mean(abs(tr_diff) >= abs(re_diff))
}) %>% do.call(what='cbind') %>% as.data.frame()
  # paste0(i,collapse = ' ')
  colnames(perm_res) = apply(vec2,MARGIN = 1, function(i) paste0(i,collapse = ' '))
  age_res[[paste0(vec[j,1],vec[j,2])]] = perm_res
}

age_res = do.call(rbind.data.frame, age_res)
# age_res
# age_res[c('data22data26','data26data31','data31data36'),]
# cerebralcortex and whitematter change across age

which(age_res <= 0.05, arr.ind = TRUE)

# apply(which(age_res <= 0.05, arr.ind = TRUE), MARGIN = 1, FUN = function(i){
#   c(rownames(age_res)[i[1]], colnames(age_res)[i[2]])
# }) %>% view()


# 22-26-31-36

# data26data31   4  14
# "CerebralNucli_R WhiteMatter_R"
```


```{r}
cor.test(data26$CerebralNucli_R, data26$WhiteMatter_R, method = 'spearman')
cor.test(data31$CerebralNucli_R, data31$WhiteMatter_R, method = 'spearman')
# cor.test(data26$CerebralNucli_R, data26$WhiteMatter_R, method = 'pearson')
# cor.test(data31$CerebralNucli_R, data31$WhiteMatter_R, method = 'pearson')
```

# Permutation test, does correlation changes across sex?

```{r}
rm(list = ls())
load(file = 'data.Rda')
data_M = filter(data,Gender == 'M')
data_F = filter(data,Gender == 'F')

library(gtools)
vec = combinations(2,2,c('data_M','data_F'))
sex_res = list()


test = function(data1,data2,i){
  l1 = dim(data1)[1]
  l2 = dim(data2)[1]
  data = c(data1[i[1]],data1[i[2]],data2[i[1]],data2[i[2]]) %>% unlist
  #shuffle
  data = sample(data,replace = F)
  cor(data[1:l1],data[(1+l1):(2*l1)], method = 'spearman')-
    cor(data[(2*l1+1):(2*l1+l2)],data[(2*l1+l2+1):(2*l1+2*l2)], method = 'spearman')
}


roi = colnames(data)[2:7]
vec2 = combinations(length(roi),2,roi)

for(j in 1:dim(vec)[1]){
  data1 = get(vec[j,1])
  data2 = get(vec[j,2])
  perm_res = lapply(1:dim(vec2)[1], function(i){
  i = vec2[i,]
  tr_diff = cor(data1[i[1]],data1[i[2]], method = 'spearman') - cor(data2[i[1]],data2[i[2]],  method = 'spearman')
  tr_diff = tr_diff %>% as.numeric()
  re_diff = replicate(10000, test(data1,data2,i))
  # hist(re_diff)
  p_value = mean(abs(tr_diff) >= abs(re_diff))
}) %>% do.call(what='cbind') %>% as.data.frame()
  # paste0(i,collapse = ' ')
  colnames(perm_res) = apply(vec2,MARGIN = 1, function(i) paste0(i,collapse = ' '))
  sex_res[[paste0(vec[j,1],vec[j,2])]] = perm_res
}

sex_res = do.call(rbind.data.frame, sex_res)
sex_res


which(sex_res <= 0.05, arr.ind = TRUE)

```


# garbage code

# mutate combine L and R together

```{r, eval = F, include=F}

library(tidyverse)
library(MRIcloudT1volumetrics)

load(file = 'raw.rda')

data = data %>% filter(type==1,level==2) %>% 
  select(rawid,roi,volume) %>% spread(roi,volume) 

# convert the rawid to be compatible with the format in lookup table
data$rawid = sapply(strsplit(data$rawid,"_"),function(x) x[1])


# only Telencephalon
data = data %>% select(rawid,CerebralCortex_L,CerebralNucli_L,WhiteMatter_L,
                        CerebralCortex_R,CerebralNucli_R,WhiteMatter_R,)

# compositional analysis

# data = data %>% lapply(function(x) as.numeric(x)) %>% as.data.frame
id = data[1]
data = cbind(data[1],prop.table(as.matrix(data[-1]), margin = 1))
data = data[-1]
data = apply(data, MARGIN = 2, FUN = function(i){ scale(i) }) %>% as.data.frame()

data_mutate = data %>% mutate(CerebralCortex = CerebralCortex_L + CerebralCortex_R) %>% mutate(CerebralNucli = CerebralNucli_L + CerebralCortex_R) %>% mutate(WhiteMatter = WhiteMatter_L + WhiteMatter_R) %>% select(CerebralCortex,CerebralNucli,WhiteMatter)

data_mutate = apply(data_mutate, MARGIN = 2, FUN = function(i){ scale(i) }) %>% as.data.frame()

data_mutate = data.frame(id,data_mutate)
ref = read.csv(paste0(getwd(),'/unrestricted_bcaffo_12_12_2017_12_17_8.csv%3B.csv'), header = T)
colnames(ref)[1] = 'rawid'

data_mutate[1] = as.numeric(unlist(data_mutate[1]))
data_mutate = left_join(data_mutate, ref[,c('rawid','Age','Gender')], by="rawid") %>% na.omit


data22 = data_mutate %>% filter(Age == '22-25')
data26 = data_mutate %>% filter(Age == '26-30')
data31 = data_mutate %>% filter(Age == '31-35')
data36 = data_mutate %>% filter(Age == '36+')
  
library(ggcorrplot)
vec = list('data22','data26','data31','data36')
lapply(vec, function(i){
  data = get(i) %>% select(-rawid,-Age,-Gender)
  ggcorrplot(cor(data, method = 'spearman'), 
             hc.order = TRUE,
             type = "lower",
             p.mat = cor_pmat(data),
             title = i,
             lab = TRUE)
})
```

# determinant of concentration matrix close to 0
# the matrix is not positive definite ~ singular


```{r,eval=F,include=F}
library(glasso)
library(qgraph)


gs = lapply(seq(0,0.00002,0.000005), function(i){
  qgraph(glasso(cov(data),rho = i),
       labels = colnames(cov(data)),
       # filetype = 'pdf',
       # filename = paste0('rho=',i),
       # layout = matrix(1:12,nrow = 4),
       # DoNotPlot = TRUE,
       details = TRUE,
       directed = TRUE)
})
# layout(matrix(c(1:6),2,3,byrow =TRUE))
# # layout.show()
# plot(gs[[1]])
# plot(gs[[2]])
# lapply(gs, plot)
```


```{r, eval = FALSE}
file.sources = list.files(c("C:/Users/lcqi/Desktop/data_analysis_bcaffo_lab/MRI_data_analysis/muvis"), 
                          pattern="*.R$", full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
library(tidyverse)
library(psych)

data(bfi)
bfi <- bfi[,1:25]
data = bfi %>% na.omit()
nhanes_dgm <- dgm(data, dtype = "gaussian", alpha = 1e-15, plot = F)

# Find the largest connected component
library(igraph)
grph_clustrs <- clusters(nhanes_dgm$graph)
new_dgm <- induced.subgraph(nhanes_dgm$graph, V(nhanes_dgm$graph)[which(grph_clustrs$membership == which.max(grph_clustrs$csize))])

# Visualize the graph
dgm_vis <- graph_vis(new_dgm, plot = F, directed = T)
dgm_vis <- graph_vis(nhanes_dgm$graph, plot = F, directed = T)
dgm_vis$network

```




